### 2021-01-25 introduction.tex
add background section , revised introduction, begin of restructuring

Previous research studies have investigated the effectiveness of mining sandboxes, using automated testing tools, to compare the performance of each tool to mine sandboxes. For instance, Bao et al. \cite{bao2018mining} present the results of an empirical study comparing 5 automated testing tools: DroidMate \cite{jamrozik2016droidmate}, Monkey \cite{Monkey}, GUIRipper \cite{amalfitano2012using}, Puma \cite{hao2014puma}, and Droidbot \cite{li2017droidbot}. The study measured the efficiency of each tool, as well as if the combination of one or more of them could lead to performance improvements. That research work consisted of performing experiments in pairs of apps, one benign and one malign (B/M), that piggybacks the corresponding benign app, leading to malicious behavior. This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, after combining 5 test generator tools, it was possible to detect 80\% of malicious behavior. Nonetheless, the field of automatic test generation of mobile apps is everything but listless---many promising automatic test generation tools have been recently proposed
~\cite{cai2020longitudinal,li2019deep}, which might outperform previous tools that have been used to mine sandboxes.

@@

In this paper, we further dig into the role of static analysis order for malware detecting. Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes. To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called droidXP \cite{dadroidxp}, whose main objective is  assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes. Our study differs from the original in the following aspects. First, we refined the dataset used, and executed the analysis of each apps, for a time biggest than the original experiment. Second, we introduced in our study, two tools that were not considered in the previous work. Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.

Thus, this paper contributes to comprehend the role of each of the analyzes in the malware detection task by:

@@

We organize the remainder of this paper as follows. Section 2 describes all the apps malware used in our experiment, presenting their characterization. Section 3 introduces the study setting of our research. Section 4 describes the benchmark solution used in our experiment. Section 5 presented some results, highlighting some motivation malware example, which will be described at Section 6. Section 7 we present the use of a promising static analysis tool, in our motivation example. Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

>>>>

Previous research studies \cite{bao2018mining} have investigated the effectiveness of mining sandboxes, using automated testing tools, comparing the performance of each tool to mine sandboxes, as well as if the combination of one or more of them could lead to performance improvements. This study indicates that the use of tools for dynamic analysis was efficient in identifying at most 70\% of the malware in a specific dataset and also reports that, even after combining all test generator tools, it was possible to detect 80\% of malicious behavior. However, this study did not focus on the possible interference of static analysis in the final result, since this study used a instrumentation tool \cite{cai2017droidfax}, that also performs a static analysis of the apps.

@@

Hence, in this paper we further dig into the role of static analysis order for malware detecting. Specifically, we aim at understanding how static analysis might be useful and help dynamic analysis in the process of mining android sandboxes. To this end, we conducted a non-exact replication of the study of Bao et al, supported by a benchmark solution, called droidXP \cite{dadroidxp}, whose main objective is assist researchers and practitioners to integrate test case generation tools and compare their performance on mining android sandboxes. Our study differs from the original in the following aspects. First, we refined the dataset used, and executed the analysis of each apps, for a time biggest than the original experiment. Second, we introduced in our study, two tools that were not considered in the previous work. Finally, we evaluate the role of each kind of analysis, static and dynamic, regarding the performance of the analyzed tools.

Altogether, this paper contributes to comprehend the role of each of the analyzes in the malware detection task by:

@@

We organize the remainder of this paper as follows. Section 2 we present a background and some related works. Section 3 describes all the apps malware used in our experiment, presenting their characterization. Section 4 introduces the study setting of our research. Section 5 presented some results, highlighting some motivation malware example. Section 6 we present the use of a promising static analysis tool, in our motivation example. Finally, Sections 7 and 8, summarizes the paper, discussing our ideas for future works, and presenting the final conclusions.

### 2021-01-25 setup.tex
add background section , revised introduction, begin of restructuring

\section{Experimental Setup}
\begin{figure*}[h!]
  \includegraphics[width=0.5\textwidth]{images/setup.png}
  \label{Experiment setup}
  \caption{Experiment setup}
  \label{fig:setup}
\end{figure*}

To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox. Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app. (Figure  \ref{fig:setup}) show all the experimental setup.

\subsection{Experiment motivation}

As described

>>>>

\section{Study Settings}

The main goal of this research work is to replicate Bao et al. study to understand the implications of static analysis algorithms in his results. We also investigate how static analysis can improve the performance of testing tools in the task of identifying malicious behaviors.

To achieve this general goal, we answer the following research questions.

\begin{enumerate}[(RQ1)]
\item What is the effective performance of each tool in terms of the number of detected malware ?
\item What benefits of using a hybrid approach, which combines static and dynamic analysis, for mining sandboxes ?
\item What is the impact of static analysis on benchmark results ?
\end{enumerate}

In the first experiment, we executed the benchmark considering 98 pairs of apps for 3 minutes. At this time, we used a new option of the benchmark that disables the static analysis performed by DroidFax. So, we used this experiment to answer the first research questions (RQ1). In the second experiment, we executed all apps with a fake tool called “Joke”, which does not do anything during the benchmark execution, to compute the results without the dynamic analysis influence. With these results, we can answer the last two research question (RQ2 and RQ3).

To assess the effectiveness of mining sandboxes created by each test case generation tools, we run these tools in benign apps and, based on resources sensitives access in this execution, we build their sandbox. Based on this sandbox, we investigate the capacity of detect malicious behaviors in the corresponding malign app. (Figure  \ref{fig:setup}) show all this experimental setup.

\subsection{Settings for RQ1}

\subsection{Settings for RQ2 and RQ3}

\begin{figure*}[h!]
  \includegraphics[width=0.5\textwidth]{images/setup.png}
  \label{Experiment setup}
  \caption{Experiment setup}
  \label{fig:setup}
\end{figure*}

\begin{figure*}[ht]
  \includegraphics[width=1\textwidth]{images/benchmark3.png}
  \label{benchArq}
  \caption{Benchmark architecture}
  \label{fig:benchArq}
\end{figure*}
